---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# mnistR

A simple R package to download, collate, and load the classic [MNIST dataset](http://yann.lecun.com/exdb/mnist/) 
in R. 

## Installation

You can install mnistR from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("itsrainingdata/mnistR")
```

## Usage

Download the data to your local drive at `/path/to`:

```{r eval = FALSE}
mnistR::downloadMNIST(dest = "/path/to/")
```

Load the data (after downloading):

```{r eval = FALSE}
mnistR::loadMNIST(dest = "/path/to/")
```

The result is a list containing two data frames (`train` and `test`). The labels are stored in the last column, `train$y` and `test$y`.

To automatically download to current working directory, extract, load, and split into train (`mnist_trn`) and test (`mnist_tst`) datasets, use:

```{r, eval = FALSE}
mnistR::autoloadMNIST()
```

## Credit

This package is a port of code written by [\@brendano](https://www.github.com/brendano) and [\@daviddalpiaz](https://www.github.com/daviddalpiaz). The original code can be found here:

* https://gist.github.com/daviddalpiaz/ae62ae5ccd0bada4b9acd6dbc9008706
* https://gist.github.com/brendano/39760
